Digital Twins for Ocean Robots

### 2024-11-17 paper/paper.tex
consolidate  section
update example to avoid warning

\author[1]{Gaël.Forget}
\affil[1]{Earth, Atmospheric and Planetary Sciences, Massachusetts Institute of Technology, \newline
77 Massachusetts Avenue, Cambridge, 02139, MA, USA}

@@

\begin{lstlisting}[
    language = Julia,
    numbers=left,
    label={lst:ArgoCode},
    caption={Download and visualize one Argo float data as in Fig.~\ref{fig:Argo_Float}.}
]
using OceanRobots, ArgoData, CairoMakie

lst=GDAC.files_list(); wmo=6900900
argo=read(ArgoFloat(),wmo=wmo,files_list=lst)

fig=plot(argo,option=:standard)
\end{lstlisting}

>>>>

\author[1]{Gaël Forget}
\affil[1]{Earth, Atmospheric and Planetary Sciences, Massachusetts Institute of Technology, \newline
77 Massachusetts Avenue, Cambridge, 02139, MA, USA}

@@

\begin{lstlisting}[
    language = Julia,
    numbers=left,
    label={lst:ArgoCode},
    caption={Download and visualize one Argo float data as in Fig.~\ref{fig:Argo_Float}.}
]
using OceanRobots, ArgoData, CairoMakie
argo=read(ArgoFloat(),wmo=6900900)
fig=plot(argo,option=:standard)
\end{lstlisting}
